\section{Introduction}

This ISR details the execution of HST COS Program 12797 - Second COS FUV Lifetime Position: FUV Target Acquisition Parameter Update (FENA4). This ISR is designed to supplement information about COS FUV spectroscopic Target Acqusitions (TAs) contained in the Instrument Handbook (IHB(v5), Holland 2012) , COS ISR 2010-014(v1) (Keyes \& Penton, ``COS Target Acquisition Guidelines, Recommendations, and Interpretation'', 2010), and COS TIR 2010-03(v1) (Penton \& Keyes, ``On-Orbit Target Acquisitions with HST+COS'', 2010).

FENA4, was the last of a series of programs allowing COS to be moved to its second lifetime position (LP2). These other programs, and what they contributed to this program, were;
\begin{itemize}
\item{12793} - FUV Detector High Voltage Sweep (FENA1)
	\begin{itemize}
	\item{Determines the initial FUV Detector High Voltage Setting for LP2.}
	\end{itemize}
\item{12795} - Verification of Aperture and FUV Spectrum Placement (FENA2)
	\begin{itemize}
	\item{Provides the cross-dispersion (XD) spectral locations for each grating.}
	\item{Provides the initial estimate for the WCA-to-PSA offsets for each grating.}
	\item{Provides the inital estimate for the XD plate scales.}
	\end{itemize}
\item{12796} - Focus Sweep Enabling Program (FENA3)
	\begin{itemize}
	\item{Determines the FUV focus settings for use during FUV spectroscopic TA.}
	\end{itemize}
\end{itemize}

bout performing FUV Spectroscopic Target Acquisitions (TAs) with the Cosmic Origins Spectrograph (COS).
